### 2024-05-31 getting-started.qmd
20240529 - add variables names
20240530 - names

```{r}
players <- data.frame(
  ID = 1:10,
  name = c(
    "Ken Cussion",
    "Ben Sacked",
    "Justin Time",
    "Lionel Scrimmage",
    "Drew Blood",
    "Hugo Long",
    "Chase Emdown",
    "Name8",
    "Name9",
    "Name10"),
  position = c("QB","QB","RB","RB","WR","WR","WR","WR","TE","TE"),
  age = c(40, 30, 20, 18, 23, 27, 32, 26, 23, NA)
  )

@@

dim(dataLong)
```

@@

dim(dataWide)
```

>>>>

```{r}
players <- data.frame(
  ID = 1:10,
  name = c(
    "Ken Cussion",
    "Ben Sacked",
    "Ron Ingback",
    "Lionel Scrimmage",
    "Drew Blood",
    "Hugo Long",
    "Chase Emdown",
    "Justin Time",
    "Name9",
    "Name10"),
  position = c("QB","QB","RB","RB","WR","WR","WR","WR","TE","TE"),
  age = c(40, 30, 20, 18, 23, 27, 32, 26, 23, NA)
  )

@@

dim(dataLong)

names(dataLong)
```

@@

dim(dataWide)

names(dataWide)
```
